---
title: "BIOL432_Assignment8"
author: "Sam Boots"
date: "15/03/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

[GitHub repository](https://github.com/SBootss/BIOL432_Assignment8)

# Setup

Loading libraries:
```{r}
library(dplyr) # For data management
library(ggplot2) # For data visualization
library(ape)
library(ggtree)
library(vegan) # tools for analyzing community ecology
```

Set default plotting theme:
```{r}
source("http://bit.ly/theme_pub")
theme_set(theme_pub())
```

Importing data:

```{r}
Data<-read.csv("./data/FloristicSurvey.csv") # importing dataset from csv (results of a floristic survey perfomed by a MSc student at Queens University Biological Station (QUBS))
```

# Checking dataset structure

```{r}
head(Data) # checking column names and variable types
```
# ANALYSIS

how the communities of plants differ across sample locations (versus tutorial, how communities of bacteria are associated w/ plant samples) 

dataset: results of a floristic survey at the Queen’s University Biological Station (QUBS).

QUESTIONS:

What effect (if any) does garlic mustard have on the plant community?

What has a stronger effect on plant communities: the presence/absence of garlic mustard (in/out) or sampling population?

Use at least one visualization for each question above and explain your reasoning.
