---
title: "BIOL432_Assignment8"
author: "Sam Boots"
date: "15/03/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

[GitHub repository](https://github.com/SBootss/BIOL432_Assignment8)

# Setup

Loading libraries:
```{r}
library(dplyr) # For data management
library(ggplot2) # For data visualization
library(ape)
library(ggtree)
library(vegan) # tools for analyzing community ecology
```

Set default plotting theme:
```{r}
source("http://bit.ly/theme_pub")
theme_set(theme_pub())
```

Importing data:

```{r}
FlorDat<-read.csv("./data/FloristicSurvey.csv") # importing dataset from csv (results of a floristic survey perfomed by a MSc student at Queens University Biological Station (QUBS))
```

# Checking dataset structure and for NA values

Checking column names and variable types:

```{r}
head(FlorDat)
```

Checking for NA values:

```{r}
sum(is.na(FlorDat))
```

# Modifying dataset

## Removing and renaming columns

Quadrate number and the counts for garlic mustard in different stages of life are not needed in further analysis, as we are interested in Sampling location and the presence and absence of garlic mustard, rather than it's abundance. "Location" was renamed to "Garlic_Mustard" to make it consistent with the later columns when converted to binary:

```{r}
FlorDat %>%
  select(2:3,11:44) %>% # removing columns
  rename("Garlic_Mustard"="Location") -> FlorDat2# renaming column
```
# Converting to binary matrix

## For Garlic Mustard Column

Changing "o" to 0 and "i" to 1, representing Garlic Mustard's presence or absence. 

```{r}
FlorDat2 %>%
  mutate(Garlic_Mustard=ifelse(Garlic_Mustard=="o",as.integer("0"),as.integer("1"))) -> FlorDat3 
head(FlorDat3)
```

## For remaining columns

```{r}
FlorDat3[,c(3:36)][FlorDat3[,c(3:36)] > 0] <- 1
head(FlorDat3) # checking correctly converted to binary matrix, leaving population column
```




